---
title: "Marriages in Toronto before and after the pandemic"
# subtitle: "My subtitle if needed"
author: 
  - Xinxiang Gao
thanks: "Code and data are available at: https://github.com/xgao28/Marriage-Licence-Statistics"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

This paper explores trends in marriage licenses in Toronto, with a focus on how the COVID-19 pandemic affected marital patterns of residents in Toronto. Utilizing a dataset of marriage license registrations from 2015 to 2023, we perform explanatory data analysis to visualize changes in marriage rates before, during, and after the pandemic. Our analysis reveals a decline in licenses issued during the pandemic, followed by a sharp rebound in the post-pandemic period, as in @fig-date. On the other hand, in general the total marriage licenses in Toronto does not reveal a boost after the pandemic. Instead, the recover is slow and steady, as in @fig-year.

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv("../data/analysis_data/analysis_data.csv")
```

The project is done by using R (@citeR) and data is retrieved open data toronto API (@opendatatoronto).

```{r}
#| label: fig-date
#| fig-cap: Number of marriage licenses over time
#| echo: false
#| warning: false
#| message: false

ggplot(data, aes(x = date, y = marriage_licenses)) +
  geom_line(color = "#2C3E50", alpha = 0.8) +  # Thicker line, custom color
  # geom_point(color = "#E74C3C", size = 2, alpha = 0.8) +   # Add points for better visibility
  labs(
    title = "Number of Marriage Licenses Over Time",
    subtitle = "An overview of trends in marriage licenses issued",
    x = "Date",
    y = "Number of Marriage Licenses"
  ) + 
  theme_minimal()
```

```{r}
#| label: fig-year
#| fig-cap: Number of total marriage licenses each year
#| echo: false
#| warning: false
#| message: false

data_g <- data %>%
  group_by(year) %>%
  summarise(total_ml = sum(marriage_licenses, na.rm = TRUE)) %>%
  ungroup()

  barplot(data_g$total_ml,
          names.arg = data_g$year,
          xlab = "Year",
          ylab = "Number of Incidents",
          main = "Incidents by Year",
          col = "skyblue")
```



\newpage


# References


